Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-02-05 tex/sections/apm.tex
Add `Selected.tex`
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The APM consists of four main modules:
\begin{itemize}
    \item \textbf{Preprocessor:} This module prepares the input data for other modules. It verifies that $H,
    P,R$ are valid w.r.t the provided commitments. It also processes the input data and ensures it has the
    correct format and is valid. For example it verifies the signatures of authenticated messages or
    checks that the proposed chunk bounds are valid.
    \item \textbf{Normal Execution Unit (NEU):} This module executes the requests whose execution completes
    normally. It outputs the updated heap chunks and an $accept_N$ flag. More formally it evaluates
    $H',accept_N=P(H,R_{good})$, where $H'$ is the updated heap chunks and $accept_N$ flag will be set to false, If an
    application terminates abruptly.
    \item \textbf{Failure Repeater Unit (FRU):} This module evaluates $accept_F=P(H',R_{bad})$, where $R_{bad}$ is
    those requests whose execution terminates abnormally, $H'$ is the output of the NEU and $accept_F$ flag is set
    to false if a request execution completes normally.

@@

@@

Assume that we have a complex component which has a considerable arithmetic circuit complexity. If this component
is needed in some arbitrary computation steps, we will need to repeat its circuit in every step of the computation. This
will increase the complexity of proof generation considerably. Fortunately, there is a workaround and instead of
repeating the circuit of the component, we can use a simpler cryptographic accumulator circuit during the
computation, and use a final verification circuit at the end to verify the functionality of the component.

@@

Interestingly, this approach can reduce the number of computation steps. When we use an accumulator circuit instead
of the component, $out$ can be available in the same computation step that $in$ is available. This will
eliminate the computation step that is needed for generating $out$ by the component's circuit.

>>>>

The APM consists of four main modules:
\begin{itemize}
    \item \textbf{Preprocessor:} This module prepares the input data for other modules. It verifies that $H,
    P,R$ are valid w.r.t the provided commitments. It also processes the input data and ensures it has the
    correct format and is valid. For example, it verifies the signatures of authenticated messages or
    checks that the proposed chunk bounds are valid.
    \item \textbf{Normal Execution Unit (NEU):} This module executes the requests whose execution completes
    normally. It outputs the updated heap chunks and an $accept_N$ flag. More formally it evaluates
    $H',accept_N=P(H,R_{good})$, where $H'$ is the updated heap chunks and $accept_N$ flag will be set to false, If an
    application terminates abruptly.
    \item \textbf{Failure Repeater Unit (FRU):} This module evaluates $accept_F=P(H',R_{bad})$, where $R_{bad}$ is
    those requests whose execution terminates abnormally, $H'$ is the output of the NEU and $accept_F$ flag is set
    to false if a request execution completes normally.

@@

\pagebreak

@@

Assume that we have a complex component which has a considerable arithmetic circuit complexity. If this component
is needed in some arbitrary computation steps, we will need to repeat its circuit in every step of the computation. This
will increase the complexity of proof generation considerably. Fortunately, there is a workaround. Instead of
repeating the circuit of the component, we can use a simpler cryptographic accumulator circuit during the
computation, and use a final verification circuit at the end to verify the functionality of the component.

@@

Interestingly, this approach can reduce the number of computation steps as well. When we use an accumulator circuit
instead of the component, $out$ can be available in the same computation step that $in$ is available. This will
eliminate the computation step that is needed for generating $out$ by the component's circuit.
